FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-08-30 ess_marmo.tex
Clarifies introduction to Section 3.

\section{Interoperable Software Developments}
\label{sec:softdev}
In section \ref{ssec:geofits} the mapping between planetary metadata concepts and
FITS metadata description has been addressed.
In order to impulse the use of FITS in planetary sciences this section will provide
some example efforts of implementation of the proposed mapping.
Our goal is, on remote sensing side, to get FITS into habits of geospatial developers,
on the other, to benefit planetary astronomers of FITS flexibility providing a processing
efficient description of their data.

>>>>

\section{Interoperable Software Developments}
\label{sec:softdev}
In section \ref{ssec:geofits} the mapping between planetary metadata concepts and
FITS metadata description has been addressed.
In order to impulse the use of FITS in planetary sciences this section will provide
some example efforts of implementation of the proposed mapping.
On remote sensing side, our goal is to get FITS into habits of geospatial developers,
improving GDAL and QGIS compatibility with FITS.
On the other side, planetary astronomers will benefit of a FITS efficient description
of their data, once the new keywords fully implemented in their traditional tools.
We provide here two examples chosen within the Europlanet VESPA collaboration.
